---
title: "EDA_Assignment2"
author: "Mastan Rao Parimi"
date: "10 September 2017"
output: html_document
---
#1)	Load the dataset early_senate_polls.csv file.
```{r, Q1}
dt <- read.csv(file = "D:/T-1/EDA/Assignment2_MAGE_MastanRaoParimi/2A/early-senate-polls.csv")
View(dt)
```
#2)	Find the number of rows and columns in the dataset
```{r, Q2}
a <- nrow(dt)
b <- ncol(dt)
cat("number of row =",a)
cat("\nnumber of columns =",b)
```
#3)	Check the class type of each column
```{r, Q3}
str(dt)
```
#4)	Use the dplyr package and
```{r, Q4}
require(dplyr)
```
#5)	For each year, calculate the average of presidential_approval
```{r, Q5}
dt %>% group_by(year) %>% summarise(avg_delay=mean(presidential_approval,na.rm=TRUE))
```
#6)	Show only the rows where the average presidential_approval obtained in the above step is greater than 100.
```{r, Q6}
dt %>% group_by(year) %>% summarise(avg_delay=mean(presidential_approval,na.rm=TRUE)) %>% filter(avg_delay>100)
```
#7)	Use the dplyr package to select the 
  a.	columns year and poll_average
  b.	For each year, find the maximum value of poll_average
```{r, Q7}
dt %>% select(year,poll_average) %>% group_by(year) %>% summarise(max_poll_avg=max(poll_average))
```
#8)	select year and election_result and arrange the results in order(ascending) of      election_result 
```{r, Q8}
dt %>% select(year,election_result) %>% arrange(election_result)
```
#9)	Use the dplyr package to select
    a.	Year and poll_average for each year
    b.	Retrieve the maximum value of poll_average and store it in a new variable       max_poll_aver.
```{r, Q9}
max_poll_aver <- dt %>% select(year,poll_average) %>% group_by(year) %>% summarise(max_poll_avg=max(poll_average))
max_poll_aver
```